More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-02-16 2016-Weak-FH-Bisim/WeakBisim.tex
added guard in the proof
clean up macros and pushed semantics (improved) to the archi paper
Guards and leaves (reu)

\newcommand{\Pred}{\symb{Pred}}
\newcommand{\Post}{\symb{Post}}
%\usepackage[math]{cellspace}
%\setlength\cellspacetoplimit{ 37pt}
%\setlength\cellspacebottomlimit{18pt}

@@

\makeatletter
\def \dotover {\textcolor{red}{\leavevmode\cleaders\hb@xt@ .22em{\hss $\cdot$\hss}\hfill\kern\z@}}
\def \reddottedrule #1#2{\hbox {\advance \hsize by -0.5em
%\sbox0{$\genfrac{}{}{0pt}{0}{#1}{#2}$} \phantom{\copy0} %
 {\ooalign{\vphantom{$\genfrac{}{}{0pt}{0}{#1}{#2}$}\cr\dotover\cr$\genfrac{}{}{0pt}{0}{#1}{#2}$\cr}}}}

 \def \dottedrule #1#2 {
  {\sbox0{$\genfrac{}{}{0pt}{0}{#1}{#2}$}%
    \vphantom{\copy0}%
    \ooalign{%
      \hidewidth
      $\vcenter{\moveright\nulldelimiterspace
        \hbox to\wd0{%
         \xleaders\hbox{\kern.5pt\vrule height 0.4pt width 1.5pt\kern.5pt}\hfill
          \kern-1.5pt
        }%
      }$
      \hidewidth\cr
    \box0\cr}}
}

\let \defaultfraction \mpr@@fraction
\makeatother

@@

% Macros for the SOS rules and proof trees:
%\newcommand\openrule[2]{\redinfer{#1}{#2}}
\newcommand\openrule[2]{\inferrule*[myfraction=\reddottedrule,center]{#1}{#2}}
%\newcommand\openrule[2]{\inferrule*{#1}{#2}}
%\newcommand\ostate[1]{\triangleleft{\;#1\;}\triangleright}
\newcommand\ostate[1]{\triangleleft{#1}\triangleright}
\newcommand{\sm}[1]{\mbox{\boldmath\small #1}}

@@

@@

\item[$\bullet$] $\symb{SV}_k^{k\in K}$ is a set of
  synchronisation vectors ($K\in\I_\P$). $\forall k\!\in\! K,
  \symb{SV}_k\!=\!\alpha_{l}^{l\in I_k \uplus J_k}\to\alpha'_k\,|\,g_k$ where
  $\alpha'_k\in \mathcal{A}_\P$, $I_k\subseteq I$, $J_k\subseteq J$,
  $\forall i\!\in\!
  I_k.\,\alpha_{i}\!\in\!\Sort(\pNet_i)$,  $\forall j\!\in\!
  J_k.\,\alpha_{j}\!\in\!\Sort_j$, and $\vars(\alpha'_k)\subseteq \bigcup_{l\in I_k\uplus 
  J_k}{\vars({\alpha_l})}$. The global action of a vector $\symb{SV}_k$ is
$\Label(\symb{SV}_k) = \alpha'_k$. $g_k \in \AlgB$ is a guard associated to the vector 
$\vars(g_k)\subseteq \bigcup_{l\in I_k\uplus J_k}{\vars({\alpha_l})}$.

@@

\item
The set of holes of a pNet is defined inductively; the sets of holes
in a pNet node and its subnets are all disjoint:
  \[\begin{array}{l}
\Holes(\mylangle S,s_0, \to\myrangle) \!=\! \emptyset\\
\Holes(\mylangle \pNet_i^{i\in I}\!,\Sort_j^{j\in J}\!, \overline{\symb{SV}}\myrangle) 
=J\uplus{\displaystyle \bigcup_{i\in 
I}\Holes(\pNet_i)}\\
\forall i\in I.\, \Holes(\pNet_i)\cap J=\emptyset\\
\forall i_1,i_2\in I.\,i_1\neq i_2\Rightarrow  \Holes(\pNet_{i_1})\cap\Holes(\pNet_{i_2})=\emptyset
\end{array}\]
\item
The set of leaves of a pNet is the set of all pLTSs occurring in the structure, defined 
inductively as:
\TODO{Nicer here at least}
\[\begin{array}{l}
\Leaves(\mylangle S,s_0, \to\myrangle) \!=\!\{\mylangle S,s_0, \to\myrangle\}\\
\Leaves(\mylangle \pNet_i^{i\in I}\!,%Sort_j^{j\in J}
\overline{\Sort}\!, \overline{\symb{SV}}\myrangle) = {\displaystyle \biguplus_{i\in 
I}\Leaves(\pNet_i)\uplus\{i\mapsto \pNet_i|\pNet_i=\pLTS\}}
\end{array}\]
\end{itemize}
\end{definition}

@@

\TODO{update pred with guards}

@@

\paragraph{Predicates:}
Let
$\mylangle\overline{\pNet},\overline{\Sort},\overline{\symb{SV}}\myrangle$
be a pNet. Consider a synchronisation vector $\symb{SV}\in \overline{\symb{SV}}$. We 
define a
predicate $\Pred$ relating
the actions of the involved sub-pNets and the resulting actions. This predicate verifies:
\[\Pred_{\symb{sv}}(SV, a_i^{i\in I}, b_j^{j\in J}, v)\Leftrightarrow \bigg(
\begin{array}{l}
\exists {(a'_i)}^{i\in I},
{(b'_j)}^{j\in J},v'.\, SV={(a'_i)}^{i\in I}, {(b'_j)}^{j\in J}\rightarrow v' | g
\\~~\land
\forall i\in I.\, a_i=a'_i\land \forall j \in J.\, b_j=b'_j \land v=v' \land g
\end{array} \bigg)\]
\LUDO{Is and g sufficient? I would say yes}

@@

	\noindent
    $\inferrule
    {k\!\in\! K \\SV_k \!=\! \alpha_m^{m \in I\uplus J} \!\to\! 
    \alpha' |g \\
    	Leaves(\mylangle \pNet_i^{i\in I}, \overline{\Sort}, \symb{SV}_k^{k\in 
    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \\    	
    	\forall m\!\!\in\!\! I. 	
    {\left(\begin{array}{l}
	{\pNet_m \models\inferrule*[myfraction=\reddottedrule]
    	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m^\prime},
    	\{\xrightarrow{b_{j}}_j\}^{j\in J'_m}, \Pred_m, \Post_m}
    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
    		\ostate{(s_i^\prime)^{i\in L_m}}}\lor }\\
		{ \pNet_m 
    	 \models
    	\inferrule*[myfraction=\reddottedrule]
    	{\{s_m \xrightarrow{v_m} s_m'\},\emptyset, \Pred_m, \Post_m}
    	{\ostate{s_m} \OTarrow {v_m}
    		\ostate{s_m'}} \land I'_m=\{m\} \land J'_m=\emptyset}
\end{array}\right)}\\
    	%\land
    	%Leaves(\pNet_m) = \overline{\pLTS}^{L_k})  	
     J' = \biguplus_{m\in I}\!\! J'_m \uplus J 	\\
    	\Pred = \bigwedge_{m\in I}\!\! \Pred_m \land
    	\Pred_{\symb{sv}}(SV_k,v_m^{m\in I},b_j^{j\in J},v)\\ 
    		I' = \biguplus_{m\in I}\!\! I_m'
    	\\\forall i\in	L\backslash I'.\,s'_i=s_i \\
    {\tt fresh}(\alpha_m,\alpha',b_j,v) 
    }
    {\mylangle \pNet_i^{i\in I}, \overline{\Sort}, \symb{SV}_k^{k\in K}\myrangle
    	\models
    	{\inferrule*[myfraction=\reddottedrule]
    		{\{s_i\xrightarrow{a_i}_i s_i^{\prime}\}^{i\in I^\prime},
    		\{\xrightarrow{b_j}_j\}^{j\in J^\prime}, \Pred, \uplus_{m\in I_k} 
    		\Post_m}
    		{\ostate{s_i^{i\in L}} \OTarrow {v}
    			\ostate{(s_i^\prime)^{i\in L}}}
    	}
    }
    $
	\medskip
%        \TODO{may be explain how $\Pred(SV,a_i^{i\in I_k},b_j^{j\in
%            J_k},v)$ is built ? You mean more than what is written on previous page????}
	%%    \TODO{I have tentatively added the sort constraint on hole actions, that was
	%%not included in the first version... I'm unsure whether this is the best place to
	%%include it, because it may change the decidability conditions on predicates}

@@

	\noindent
    $\inferrule
    {k\!\in\! K \\SV_k \!=\! \alpha_m^{m \in I\uplus J} \!\to\! 
    \alpha' |g \\
    	Leaves(\mylangle \pNet_i^{i\in I}, \overline{\Sort}, \symb{SV}_k^{k\in 
    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \\    	
    	\forall m\!\!\in\!\! I. 	
    {\left(\begin{array}{l}
	{\pNet_m \models\inferrule*[myfraction=\reddottedrule]
    	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m^\prime},
    	\{\xrightarrow{b_{j}}_j\}^{j\in J'_m}, \Pred_m, \Post_m}
    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
    		\ostate{(s_i^\prime)^{i\in L_m}}}\lor }\\
		{ \pNet_m 
    	 \models
    	\inferrule*[myfraction=\reddottedrule]
    	{\{s_m \xrightarrow{v_m} s_m'\},\emptyset, \Pred_m, \Post_m}
    	{\ostate{s_m} \OTarrow {v_m}
    		\ostate{s_m'}} \land I'_m=\{m\} \land J'_m=\emptyset}
\end{array}\right)}\\
    	%\land
    	%Leaves(\pNet_m) = \overline{\pLTS}^{L_k})  	
     J' = \biguplus_{m\in I}\!\! J'_m \uplus J 	\\
    	\Pred = \bigwedge_{m\in I}\!\! \Pred_m \land
    	\Pred_{\symb{sv}}(SV_k,v_m^{m\in I},b_j^{j\in J},v)\\ 
    		I' = \biguplus_{m\in I}\!\! I_m'
    	\\\forall i\in	L\backslash I'.\,s'_i=s_i \\
    {\tt fresh}(\alpha_m,\alpha',b_j,v) 
    }
    {\mylangle \pNet_i^{i\in I}, \overline{\Sort}, \symb{SV}_k^{k\in K}\myrangle
    	\models
    	{\inferrule*[myfraction=\reddottedrule]
    		{\{s_i\xrightarrow{a_i}_i s_i^{\prime}\}^{i\in I^\prime},
    		\{\xrightarrow{b_j}_j\}^{j\in J^\prime}, \Pred, \uplus_{m\in I_k} 
    		\Post_m}
    		{\ostate{s_i^{i\in L}} \OTarrow {v}
    			\ostate{(s_i^\prime)^{i\in L}}}
    	}
    }
    $
	\medskip

@@

This already ensures the second part of the conclusion of the lemma, i.e. the OT for $Q$ 
if we 
choose\footnotemark[\thefootnote]  $v_Q=v_{j_0}$ ($\Pred\,''= \Pred_{j_0}$). Considering 
the OT of $P$ let $I'= 
\biguplus I'_m=I\setminus L_Q$, $J'=\biguplus J'_m\uplus J
\uplus\{j_0\}=J\setminus\Holes(Q)\uplus \{j_0\}$;  the predicate is 
$\Pred\,'=\bigwedge_{m\in I_k}\Pred_m  \land \Pred_{\symb{sv}}(SV_k,v_m^{m\in 
I},b_j^{j\in J\cup \{j_0\}},v)$
where\footnotemark[\thefootnote] $\Pred_{\symb{sv}}(SV_k,v_m^{m\in I},b_j^{j\in J\cup 
\{j_0\}},v)\Leftrightarrow 
\forall i\in I_k.\, \alpha_i=a_i\land \forall j \in J\cup \{j_0\}.\, \alpha_j=b_j \land 
v=\alpha'
$. Modulo renaming of fresh variables, this is identical to the predicate that occurs in 
the source open transition except $\alpha_{j_0}=v_{j_0}$ has been replaced by  
$\alpha_{j_0}=b_{j_0}$.
Thus, $\Pred\subst{v_Q\leftarrow b_{j_0}}=(\Pred\,' 
\land \Pred\,'')$. %\TODO{the argument on renaming has mostly been
                 %removed is it still OK? yes.}. 
Finally, Post 
%conditions are easily split\footnote{\TODO{moved. could
%    even remove...?}Note that if the rules are not simplified, no
%  post-condition range over the variables of $P$ and $Q$ at the same
%  time} 
into conditions of the context $P$ and the pNet $Q$ (they are
builts similarly as they only deal with  
leaves): $\Post=\Post\,'\uplus \Post\,''$. This concludes the 
proof as we checked all the premises of the open transition for both $P$ and $Q$.\qed
\footnotetext{Cloning and freshness introduce alpha-conversion at many points 
of the proof; we 
	only 
	give major arguments concerning alpha-conversion to make the proof readable; in 
	general, fresh variables appear in each transition inside
        terms $b_j$, $v$, and 
	$\Pred$.}
\end{proof}
   \end{small}

@@

Lemma \ref{lem-compose} is combining an open transition of $P$ with
an open transition of $Q$, and building a corresponding transition of
$P[Q]_{j_0}$, assembling their predicates.

\begin{lemma}[Open transition composition]\label{lem-compose} 
	Suppose $j_0\in J$ and:\\[-2ex]
\begin{mathpar}
%\[
P\models{\inferrule*[myfraction=\reddottedrule]
	{\{s_i\xrightarrow{a_i}_i s_i'\}^{i\in I},
		\{\xrightarrow{b_j}_j\}^{j\in J}, \\\\
		\Pred,  
		\Post}
	{\ostate{s_i^{i\in L}} \OTarrow {v}
		\ostate{s_i'^{\, i\in L}}}
}%\]
\text{~and~}
%\[
Q\models{\inferrule*[myfraction=\reddottedrule]
	{\{s_i\xrightarrow{a_i}_i s_i'\}^{i\in I_Q},
		\{\xrightarrow{b_j}_j\}^{j\in J_Q},\\\\
		 \Pred\,',  
		\Post\,'}
	{\ostate{s_i^{i\in L_Q}} \OTarrow {v_Q}
		\ostate{s_i'^{\, i\in L_Q}}}
}%\]
\end{mathpar}
Then, we have\\[-2ex]
	\[ P[Q]_{j_0}  
	\models
	{\inferrule*[myfraction=\reddottedrule]
		{\{s_i\xrightarrow{a_i}_i s_i^{\prime}\}^{i\in I \uplus I_Q},
			\{\xrightarrow{b_j}_j\}^{(j\in J\setminus\{j_0\}) \uplus J_Q}, 
			\Pred\subst{b_{j_0}\leftarrow v_Q}\land\Pred\,',  
			\Post\uplus \Post\,'}
		{\ostate{s_i^{i\in L\uplus L_Q}} \OTarrow {v}
			\ostate{s_i'^{\, i\in L\uplus L_Q}}}
	}
	\]
\end{lemma}
\begin{small}

>>>>

%\usepackage[math]{cellspace}
%\setlength\cellspacetoplimit{ 37pt}
%\setlength\cellspacebottomlimit{18pt}

@@

@@

@@

\TODO{state clearly that the next two definitions are mutually dependent}

@@

\item[$\bullet$] $\symb{SV}_k^{k\in K}$ is a set of
  synchronisation vectors ($K\in\I_\P$). $\forall k\!\in\! K,
  \symb{SV}_k\!=\!\alpha_{l}^{l\in I_k \uplus J_k}\to\alpha'_k\,|\,e_k$ where
  $\alpha'_k\in \mathcal{A}_\P$, $I_k\subseteq I$, $J_k\subseteq J$,
  $\forall i\!\in\!
  I_k.\,\alpha_{i}\!\in\!\Sort(\pNet_i)$,  $\forall j\!\in\!
  J_k.\,\alpha_{j}\!\in\!\Sort_j$, and $\vars(\alpha'_k)\subseteq \bigcup_{l\in I_k\uplus 
  J_k}{\vars({\alpha_l})}$. The global action of a vector $\symb{SV}_k$ is
$\alpha'_k$. $e_k \in \AlgB$ is a guard associated to the vector 
$\vars(e_k)\subseteq \bigcup_{l\in I_k\uplus J_k}{\vars({\alpha_l})}$.

@@

\item
The set of holes of a pNet is defined inductively; the sets of holes
in a pNet node and its subnets are all disjoint:
  \[\begin{array}{l}
\Holes(\mylangle S,s_0, \to\myrangle) \!=\! \emptyset\\
\Holes(\mylangle \pNet_i^{i\in I}\!,\Sort_j^{j\in J}\!, \overline{\symb{SV}}\myrangle) 
=J\uplus{\displaystyle \bigcup_{i\in 
I}\Holes(\pNet_i)}\\
\forall i\in I.\, \Holes(\pNet_i)\cap J=\emptyset\\
\forall i_1,i_2\in I.\,i_1\neq i_2\Rightarrow  \Holes(\pNet_{i_1})\cap\Holes(\pNet_{i_2})=\emptyset
\end{array}\]
\item
The set of leaves of a pNet is the set of all pLTSs occurring in the structure, defined 
inductively as:
\[\begin{array}{l}
\Leaves(\mylangle S,s_0, \to\myrangle) \!=\!\{\mylangle S,s_0, \to\myrangle\}\\
\Leaves(\mylangle \pNet_i^{i\in I}\!,%Sort_j^{j\in J}
\overline{\Sort}\!, \overline{\symb{SV}}\myrangle) = {\displaystyle \biguplus_{i\in 
I}\Leaves(\pNet_i)\uplus\{i\mapsto \pNet_i|\pNet_i \text{ is a }\pLTS\}}
\end{array}\]
\end{itemize}
\end{definition}

@@

@@

\paragraph{Predicates:}
Let
$\mylangle\overline{\pNet},\overline{\Sort},\overline{\symb{SV}}\myrangle$
be a pNet. Consider a synchronisation vector $\symb{SV}\in \overline{\symb{SV}}$. We 
define a
predicate $\Pred$ relating
the actions of the involved sub-pNets and the resulting actions. This predicate verifies:
\[\Pred_{\symb{sv}}(SV, a_i^{i\in I}, b_j^{j\in J}, v)\Leftrightarrow \bigg(
\begin{array}{l}
\exists {(a'_i)}^{i\in I},
{(b'_j)}^{j\in J},v'.\, SV={(a'_i)}^{i\in I}, {(b'_j)}^{j\in J}\rightarrow v' | e_b
\\~~\land
\forall i\in I.\, a_i=a'_i\land \forall j \in J.\, b_j=b'_j \land v=v' \land e_b
\end{array} \bigg)\]
\LUDO{Is and g sufficient? I would say yes}

@@

	\noindent
    $\inferrule
    {k\!\in\! K \\SV_k \!=\! \alpha_m^{m \in I\uplus J} \!\to\! 
    \alpha' |e_b \\
    	Leaves(\mylangle \pNet_i^{i\in I}, \overline{\Sort}, \symb{SV}_k^{k\in 
    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \\    	
    	\forall m\!\!\in\!\! I. 	
    {\left(\begin{array}{l}
	{\pNet_m \models\inferrule*[myfraction=\reddottedrule]
    	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m^\prime},
    	\{\xrightarrow{b_{j}}_j\}^{j\in J'_m}, \Pred_m, \Post_m}
    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
    		\ostate{(s_i^\prime)^{i\in L_m}}}\lor }\\
		{ \pNet_m 
    	 \models
    	\inferrule*[myfraction=\reddottedrule]
    	{\{s_m \xrightarrow{v_m} s_m'\},\emptyset, \Pred_m, \Post_m}
    	{\ostate{s_m} \OTarrow {v_m}
    		\ostate{s_m'}} \land I'_m=\{m\} \land J'_m=\emptyset}
\end{array}\right)}\\
    	%\land
    	%Leaves(\pNet_m) = \overline{\pLTS}^{L_k})  	
     J' = \biguplus_{m\in I}\!\! J'_m \uplus J 	\\
    	\Pred = \bigwedge_{m\in I}\!\! \Pred_m \land
    	\Pred_{\symb{sv}}(SV_k,v_m^{m\in I},b_j^{j\in J},v)\\ 
    		I' = \biguplus_{m\in I}\!\! I_m'
    	\\\forall i\in	L\backslash I'.\,s'_i=s_i \\
    {\tt fresh}(\alpha_m,\alpha',b_j,v) 
    }
    {\mylangle \pNet_i^{i\in I}, \overline{\Sort}, \symb{SV}_k^{k\in K}\myrangle
    	\models
    	{\inferrule*[myfraction=\reddottedrule]
    		{\{s_i\xrightarrow{a_i}_i s_i^{\prime}\}^{i\in I^\prime},
    		\{\xrightarrow{b_j}_j\}^{j\in J^\prime}, \Pred, \uplus_{m\in I_k} 
    		\Post_m}
    		{\ostate{s_i^{i\in L}} \OTarrow {v}
    			\ostate{(s_i^\prime)^{i\in L}}}
    	}
    }
    $
	\medskip
%        \TODO{may be explain how $\Pred(SV,a_i^{i\in I_k},b_j^{j\in
%            J_k},v)$ is built ? You mean more than what is written on previous page????}
	%%    \TODO{I have tentatively added the sort constraint on hole actions, that was
	%%not included in the first version... I'm unsure whether this is the best place to
	%%include it, because it may change the decidability conditions on predicates}

@@

	\noindent
    $\inferrule
    {k\!\in\! K \\SV_k \!=\! \alpha_m^{m \in I\uplus J} \!\to\! 
    \alpha' |e_b \\
    	Leaves(\mylangle \pNet_i^{i\in I}, \overline{\Sort}, \symb{SV}_k^{k\in 
    	K}\myrangle) \!=\! \pLTS_l^{l\in L} \\    	
    	\forall m\!\!\in\!\! I. 	
    {\left(\begin{array}{l}
	{\pNet_m \models\inferrule*[myfraction=\reddottedrule]
    	{\{s_{i}\xrightarrow{a_{i}}_i s_{i}'\}^{i\in I_m^\prime},
    	\{\xrightarrow{b_{j}}_j\}^{j\in J'_m}, \Pred_m, \Post_m}
    	{\ostate{s_{i}^{i \in L_m}} \OTarrow {v_m}
    		\ostate{(s_i^\prime)^{i\in L_m}}}\lor }\\
		{ \pNet_m 
    	 \models
    	\inferrule*[myfraction=\reddottedrule]
    	{\{s_m \xrightarrow{v_m} s_m'\},\emptyset, \Pred_m, \Post_m}
    	{\ostate{s_m} \OTarrow {v_m}
    		\ostate{s_m'}} \land I'_m=\{m\} \land J'_m=\emptyset}
\end{array}\right)}\\
    	%\land
    	%Leaves(\pNet_m) = \overline{\pLTS}^{L_k})  	
     J' = \biguplus_{m\in I}\!\! J'_m \uplus J 	\\
    	\Pred = \bigwedge_{m\in I}\!\! \Pred_m \land
    	\Pred_{\symb{sv}}(SV_k,v_m^{m\in I},b_j^{j\in J},v)\\ 
    		I' = \biguplus_{m\in I}\!\! I_m'
    	\\\forall i\in	L\backslash I'.\,s'_i=s_i \\
    {\tt fresh}(\alpha_m,\alpha',b_j,v) 
    }
    {\mylangle \pNet_i^{i\in I}, \overline{\Sort}, \symb{SV}_k^{k\in K}\myrangle
    	\models
    	{\inferrule*[myfraction=\reddottedrule]
    		{\{s_i\xrightarrow{a_i}_i s_i^{\prime}\}^{i\in I^\prime},
    		\{\xrightarrow{b_j}_j\}^{j\in J^\prime}, \Pred, \uplus_{m\in I_k} 
    		\Post_m}
    		{\ostate{s_i^{i\in L}} \OTarrow {v}
    			\ostate{(s_i^\prime)^{i\in L}}}
    	}
    }
    $
	\medskip

@@

This already ensures the second part of the conclusion of the lemma, i.e. the OT for $Q$ 
if we 
choose\footnotemark[\thefootnote]  $v_Q=v_{j_0}$ ($\Pred\,''= \Pred_{j_0}$). Considering 
the OT of $P$ let $I'= 
\biguplus I'_m=I\setminus L_Q$, $J'=\biguplus J'_m\uplus J
\uplus\{j_0\}=J\setminus\Holes(Q)\uplus \{j_0\}$;  the predicate is 
$\Pred\,'=\bigwedge_{m\in I_k}\Pred_m  \land \Pred_{\symb{sv}}(SV_k,v_m^{m\in 
I},b_j^{j\in J\cup \{j_0\}},v)$
where\footnotemark[\thefootnote] $\Pred_{\symb{sv}}(SV_k,v_m^{m\in I},b_j^{j\in J\cup 
\{j_0\}},v)\Leftrightarrow 
\forall i\in I_k.\, \alpha_i=a_i\land \forall j \in J\cup \{j_0\}.\, \alpha_j=b_j \land 
v=\alpha'
\land g$. Modulo renaming of fresh variables, this is identical to the predicate that 
occurs in 
the source open transition except $\alpha_{j_0}=v_{j_0}$ has been replaced by  
$\alpha_{j_0}=b_{j_0}$.
Thus, $\Pred\subst{v_Q\leftarrow b_{j_0}}=(\Pred\,' 
\land \Pred\,'')$. %\TODO{the argument on renaming has mostly been
                 %removed is it still OK? yes.}. 
Finally, Post 
%conditions are easily split\footnote{\TODO{moved. could
%    even remove...?}Note that if the rules are not simplified, no
%  post-condition range over the variables of $P$ and $Q$ at the same
%  time} 
into conditions of the context $P$ and the pNet $Q$ (they are
builts similarly as they only deal with  
leaves): $\Post=\Post\,'\uplus \Post\,''$. This concludes the 
proof as we checked all the premises of the open transition for both $P$ and $Q$.\qed
\footnotetext{Cloning and freshness introduce alpha-conversion at many points 
of the proof; we 
	only 
	give major arguments concerning alpha-conversion to make the proof readable; in 
	general, fresh variables appear in each transition inside
        terms $b_j$, $v$, and 
	$\Pred$.}
\end{proof}
   \end{small}

@@

Lemma \ref{lem-compose} is combining an open transition of $P$ with
an open transition of $Q$, and building a corresponding transition of
$P[Q]_{j_0}$, assembling their predicates.
\TODO{LUDO: REPROVE}
\begin{lemma}[Open transition composition]\label{lem-compose} 
	Suppose $j_0\in J$ and:\\[-2ex]
\begin{mathpar}
%\[
P\models{\inferrule*[myfraction=\reddottedrule]
	{\{s_i\xrightarrow{a_i}_i s_i'\}^{i\in I},
		\{\xrightarrow{b_j}_j\}^{j\in J}, \\\\
		\Pred,  
		\Post}
	{\ostate{s_i^{i\in L}} \OTarrow {v}
		\ostate{s_i'^{\, i\in L}}}
}%\]
\text{~and~}
%\[
Q\models{\inferrule*[myfraction=\reddottedrule]
	{\{s_i\xrightarrow{a_i}_i s_i'\}^{i\in I_Q},
		\{\xrightarrow{b_j}_j\}^{j\in J_Q},\\\\
		 \Pred\,',  
		\Post\,'}
	{\ostate{s_i^{i\in L_Q}} \OTarrow {v_Q}
		\ostate{s_i'^{\, i\in L_Q}}}
}%\]
\end{mathpar}
Then, we have\\[-2ex]
	\[ P[Q]_{j_0}  
	\models
	{\inferrule*[myfraction=\reddottedrule]
		{\{s_i\xrightarrow{a_i}_i s_i^{\prime}\}^{i\in I \uplus I_Q},
			\{\xrightarrow{b_j}_j\}^{(j\in J\setminus\{j_0\}) \uplus J_Q}, 
			\Pred\subst{b_{j_0}\leftarrow v_Q}\land\Pred\,',  
			\Post\uplus \Post\,'}
		{\ostate{s_i^{i\in L\uplus L_Q}} \OTarrow {v}
			\ostate{s_i'^{\, i\in L\uplus L_Q}}}
	}
	\]
\end{lemma}
\begin{small}
